---
title: "endoR: multiclass"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{endoR: multiclass}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 2.5
)
```

This vignette illustrates how to interpret multiclass models with endoR. 
We will use the iris data for this purpose: the species is being predicted 
(= target) using the length and width of petals and sepals (= features).  

# Preambule
```{r setup, message = FALSE, warning=FALSE}
library(endoR)
library(randomForest)
library(tidyverse)
library(caret)
library(ggpubr)
library(ggraph)
```

# Data
```{r}
data(iris)
summary(iris)
```

# Fit model
```{r}
set.seed(1313)
mod <- randomForest(Species ~ ., data = iris)
mod
```

# Fit endoR for the "setosa" species

We will only prune (= TRUE) and discretize decisions in K = 3 levels.
```{r}
endo_setosa <- model2DE(model = mod, model_type = 'rf'
                 , data = select(iris, -Species), target = iris$Species
                 , classPos = 'setosa' # our focal class
                 , filter = FALSE 
                 
                 # we filter in K = 3 categories the numerical features
                 , discretize = TRUE, K = 3)
```

Plants from the setosa species have small petals and narrow, long sepals. 
```{r}
plotFeatures(endo_setosa, levels_order = c('Low', 'Medium', 'High'))

# The warnings du to the font are due to Windows .. no worries.
plotNetwork(endo_setosa, hide_isolated_nodes = FALSE, layout = 'fr')
```

The only interaction used for predictions is the one of sepal length (High = 
long) and width (Low = narrow). We can also use ggplot2 `theme` to format the 
plot, e.g., put the legend boxes next to each other.
```{r}
plotNetwork(endo_setosa, hide_isolated_nodes = TRUE, layout = 'fr')+
  theme(legend.box = "horizontal")
```


# Fit endoR for the "versicolor" species

This time we will filter decisions based on their importance to trim the network 
(filter = TRUE). We will use min_imp = 0.5 to keep at least all decisions with 
an importance > 0.5*the best importance (the lower min_imp, the slighter the 
filtering).

```{r}
endo_versicolor <- model2DE(model = mod, model_type = 'rf'
                 , data = select(iris, -Species), target = iris$Species
                 , classPos = 'versicolor'
                 , K = 3, discretize = TRUE
                 , filter = TRUE, min_imp = 0.5)
```


The petal's proportions are intermediary compared to the setosa and virginica
species. 
```{r}
plotFeatures(endo_versicolor, levels_order = c('Low', 'Medium', 'High'))
```

Sepals have a narrow-intermediary width and long-intermediary length
(= if wide and small then it's not a versicolor, as seen on the network).
```{r}
plotNetwork(endo_versicolor, hide_isolated_nodes = FALSE, layout = 'fr'
            # we show only edges that connect 3 nodes max -> removes edges with 
            # lowest importances - for longer paths = more complex network,
            # you can increase path_length
            , path_length = 3  
            )+
  scale_edge_alpha(range = c(0.8,1))+
  theme(legend.box = "horizontal")
```
